\documentclass[a4paper]{article}
\usepackage[margin=1in, paperwidth=5.5in, paperheight=8.5in]{geometry}
%\usepackage{geometry}
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{natbib}

\usepackage{hyperref}
\usepackage{hypcap}
\usepackage{tikz}
%\usepackage{mdframed}
\usetikzlibrary{shapes,arrows}

\usepackage{enumerate}
\usepackage{ifthen}
\usepackage{environ}

\makeatletter
\NewEnviron{solution}[1][true]{
  \gdef\@tmp{#1}
  \ifthenelse{\boolean{#1}}{\par{ \textcolor{red}{\\ \textbf{Suggested Solution:}}\\}\par\BODY}{\ignorespaces}
}[\ifthenelse{\boolean{\@tmp}}{}{\ignorespacesafterend}]
\makeatother    


\newcommand{\solon}{true}

\bibpunct{(}{)}{,}{a}{}{;}

\hypersetup{
colorlinks=true
}
\parindent 0in
%\usepackage{fancyhdr} 
%\pagestyle{fancy} 

\usepackage{enumerate,letltxmacro}
\LetLtxMacro\itemold\item
\renewcommand{\item}{\itemindent1cm\itemold}

\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}


%adjustment of page parameters
\renewcommand{\baselinestretch}{1.50} % line spacing is set 1.5
\setlength{\textheight}{8.8in} \setlength{\textwidth}{6.3in}
\setlength{\oddsidemargin}{0.2in} \setlength{\topmargin}{-0.30in}
\setlength{\footnotesep}{10.0pt}
\setlength\parindent{0pt}
\title{{\Large \bf Homework \#3: Growth and Intertemporal Tradeoff} \\ \small Econ 590: Current Topics in Macro \\ \small Due at 11:59 p.m., Friday of Third Week}
\date{}
\usepackage{ifthen}
\usepackage{environ}


\usepackage{accsupp}


\begin{document}
\maketitle
 
\noindent
\textbf{Choose one of these prompts to respond to.  I ask that you respond to the prompt you \emph{disagree} with.  E.g. if you think there should be more immigration in the U.S., make the strongest case \emph{against} immigration.  If you think there should be less, state the strongest case \emph{for} immigration.  }\\

\section*{For: Increased Immigration in the United States}
Please write a page trying to convince someone \emph{not on purely moral grounds} to increase immigration in the United States.  Your argument should use cited facts, either from the lecture or from outside the lecture (hyperlink is fine).  Target Audience: a US President opposed to immigration but open to facts.\\
\ \\

\section*{Against: decreased immigration in the United States}
Please write a page trying to convince someone \emph{not on purely moral grounds} to decrease or halt immigration in the United States.  Your argument should use cited facts, either from the lecture or from outside the lecture  (hyperlink is fine).  Target Audience: a liberal/libertarian who only sees benefit from immigration.\\
\ \\


\end{document}