\documentclass[a4paper]{article}
\usepackage[margin=1in, paperwidth=5.5in, paperheight=8.5in]{geometry}
%\usepackage{geometry}
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{natbib}

\usepackage{hyperref}
\usepackage{hypcap}
\usepackage{tikz}
%\usepackage{mdframed}
\usetikzlibrary{shapes,arrows}

\usepackage{enumerate}
\usepackage{ifthen}
\usepackage{environ}

\makeatletter
\NewEnviron{solution}[1][true]{
  \gdef\@tmp{#1}
  \ifthenelse{\boolean{#1}}{\par{ \textcolor{red}{\\ \textbf{Suggested Solution:}}\\}\par\BODY}{\ignorespaces}
}[\ifthenelse{\boolean{\@tmp}}{}{\ignorespacesafterend}]
\makeatother    


\newcommand{\solon}{true}

\bibpunct{(}{)}{,}{a}{}{;}

\hypersetup{
colorlinks=true
}
\parindent 0in
%\usepackage{fancyhdr} 
%\pagestyle{fancy} 

\usepackage{enumerate,letltxmacro}
\LetLtxMacro\itemold\item
\renewcommand{\item}{\itemindent1cm\itemold}

\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}


%adjustment of page parameters
\renewcommand{\baselinestretch}{1.50} % line spacing is set 1.5
\setlength{\textheight}{8.8in} \setlength{\textwidth}{6.3in}
\setlength{\oddsidemargin}{0.2in} \setlength{\topmargin}{-0.30in}
\setlength{\footnotesep}{10.0pt}
\setlength\parindent{0pt}
\title{{\Large \bf Homework \#1: GDP} \\ \small Econ 590: Current Topics in Macro \\ \small Due at  11:59 p.m. EDT of Friday, First Week}
\date{}
\usepackage{ifthen}
\usepackage{environ}


\usepackage{accsupp}


\begin{document}
\maketitle
 
\noindent
(1). Pick a country of interest to you that no more than one other person in the class picks.\footnote{If more than two people pick the country, all parties lose one point out of twenty.  Coordinate/equilibrate however you wish.  Coordination and the use of discussion is part of the homework.}\\
\ \\
(2) Write one to two pages (excluding any figures or tables) about the path of GDP in that country over time.  Answer the question: ``Have GDP measurements accurately reflected happiness or progress in that country over time?"  A good argument might include references to other aggregates and data (employment, investment, export/imports, consumption, happiness data, etc.).\\
\ \\
You will be graded on how clear your answer to the question is.   This means not only should you reference data, but the data should be in such a format that your argument is clear (e.g. a clear figure or set of figures that tells a tale).  \\
\ \\
Things to remember:
\begin{itemize}
\item Don't repeat yourself unnecessarily
\item Figures $>$ tables
\item Your own data analysis $>>$ a figure copied/pasted from online
\item A well-argued or interesting point is king
\item Being succinct and clear is crucial
\item Don't repeat yourself unnecessarily
\end{itemize}

\end{document}